### 2013-06-27 latex/SupportingText.tex
Updated Supporting Text.

\bigskip
\begin{center}
Matthew A. Tien, Austin G. Meyer, Stephanie J. Spielman, Claus O. Wilke
\end{center}
\bigskip

\subsection*{Supporting Figures}
%\centerline{\includegraphics[width=3.5in]{figures/Ala_dist.png}}

@@

@@

\noindent Table S1. Backbone conformation of maximally exposed trimer structures. Multiple rows per residue indicate alternative conformations with comparable solvent exposure.

\begin{center}
\footnotesize
\begin{tabular}{lccccccccc}
Residue & max-emp-100 & max-emp-97 & max-emp-80 & max-emp-gen & & max-theo-100 & max-theo-97 & max-theo-80 & max-theo-gen\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $129$ & $128$ & $132$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $274$ & $274$ & $280$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $195$ & $193$ & $199$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $193$ & $192$ & $197$\\
Cysteine         & $148$ & $148$ & $133$ & $148$ & & $169$ & $167$ & $157$ & $167$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $223$ & $222$ & $227$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $225$ & $224$ & $228$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $104$ & $104$ & $109$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $213$ & $209$ & $209$ & $209$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $197$ & $196$ & $201$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $201$ & $199$ & $205$\\
Lysine           & $230$ & $230$ & $229$ & $230$ & & $246$ & $236$ & $235$ & $240$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $224$ & $218$ & $226$\\
Phenylalanine    & $228$ & $228$ & $226$ & $228$ & & $251$ & $240$ & $236$ & $244$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $159$ & $157$ & $164$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $155$ & $150$ & $158$\\
Threonine        & $163$ & $163$ & $161$ & $163$ & & $182$ & $172$ & $171$ & $176$\\
Tryptophan       & $264$ & $264$ & $262$ & $264$ & & $295$ & $285$ & $282$ & $293$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $263$ & $262$ & $266$\\
Valine           & $166$ & $165$ & $165$ & $166$ & & $184$ & $174$ & $173$ & $177$\\
\hline
\end{tabular}
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lcccccccc}
Residue & pop-97 & pop-80 \\
\hline Alanine   & $4$ & $47$ \\
Arginine         & $2$ & $23$ \\
Asparagine       & $2$ & $15$ \\
Aspartate        & $3$ & $20$ \\
Cysteine         & $0$ & $\phantom{0}5$ \\
Glutamate        & $3$ & $34$ \\
Glutamine        & $2$ & $18$ \\
Glycine          & $2$ & $15$ \\
Histidine        & $1$ & $\phantom{0}9$ \\
Isoleucine       & $6$ & $40$ \\
Leucine          & $7$ & $59$ \\
Lysine           & $3$ & $27$ \\
Methionine       & $0$ & $\phantom{0}8$ \\
Phenylalanine    & $2$ & $20$ \\
Proline          & $7$ & $80$ \\
Serine           & $2$ & $27$ \\
Threonine        & $3$ & $33$ \\
Tryptophan       & $0$ & $\phantom{0}8$ \\
Tyrosine         & $2$ & $18$ \\
Valine           & $7$ & $50$ \\
\hline
\end{tabular}
\end{center}

@@

\newpage
\noindent Table S2. Hydrophobicity scales derived in this work.
\bigskip

@@

%\centerline{\includegraphics[width=3.5in]{figures/atom_placement}}
\noindent {\small Schematic drawing of the placement of an atom relative to three reference atoms A, B, and C. Atom C is assumed to be at the origin. The vector from C to B is denoted by $\mathbf{b}$, with coordinates $(x_\mathbf{b}, y_\mathbf{b}, z_\mathbf{b})$. Similarly, the vector from C to A is denoted by $\mathbf{a}$, with coordinates $(x_\mathbf{a}, y_\mathbf{a}, z_\mathbf{a})$. The distance from C to X is $\ell$, the angle between CB and CX is $\theta$, and the dihedral angle between ABC and CX is $\tau$.}
\bigskip

>>>>

\bigskip
\noindent Matthew A. Tien, Austin G. Meyer, Dariya K. Sydykova, Stephanie J. Spielman, Claus O. Wilke

\bigskip

\subsection*{Supporting Figures}
\centerline{\includegraphics[width=3.5in]{figures/Alanine_RSA_distribution.pdf}}

@@

\newpage
\centerline{\includegraphics[width=6in]{figures/Ala_Rama_HSV_ALL_edited.pdf}}

\noindent Figure S2. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All non-empty bins are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for non-empty bins in (A).

\vspace*{.5in}

\centerline{\includegraphics[width=6in]{figures/Ala_Rama_HSV_GENEROUS_edited.pdf}}

\noindent Figure S3. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All non-empty bins in the GENEROUS regions are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for all bins in the GENEROUS region.

\centerline{\includegraphics[width=6in]{figures/Ala_Rama_HSV_CORE_edited.pdf}}

\noindent Figure S4. Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All bins in the CORE region are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for all bins in the CORE region.

@@

\noindent Table S1. Maximum SA values observed in the empirical and the theoretical data sets.

\begin{center}
\scriptsize
\begin{tabular}{lccccccccc}
 & \multicolumn{4}{c}{Empirical} &&\multicolumn{4}{c}{Theoretical}\\\cline{2-5}\cline{7-10}\\[-1.6ex]
Residue          & ALL & GENEROUS & ALLOWED & CORE & & ALL & GENEROUS & ALLOWED & CORE\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $132$ & $129$ & $128$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $280$ & $274$ & $274$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $199$ & $195$ & $193$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $197$ & $193$ & $192$\\
Cysteine         & $148$ & $148$ & $148$ & $133$ & & $169$ & $167$ & $167$ & $157$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $227$ & $223$ & $222$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $228$ & $225$ & $224$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $109$ & $104$ & $104$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $213$ & $209$ & $209$ & $209$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $201$ & $197$ & $196$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $205$ & $201$ & $199$\\
Lysine           & $230$ & $230$ & $230$ & $229$ & & $246$ & $240$ & $236$ & $235$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $226$ & $224$ & $218$\\
Phenylalanine    & $228$ & $228$ & $228$ & $226$ & & $251$ & $244$ & $240$ & $236$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $164$ & $159$ & $157$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $158$ & $155$ & $150$\\
Threonine        & $163$ & $163$ & $163$ & $161$ & & $182$ & $176$ & $172$ & $171$\\
Tryptophan       & $264$ & $264$ & $264$ & $262$ & & $295$ & $293$ & $285$ & $282$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $266$ & $263$ & $262$\\
Valine           & $166$ & $166$ & $165$ & $165$ & & $184$ & $177$ & $174$ & $173$\\
\hline
\end{tabular}
\end{center}

\bigskip

\noindent Table S2. Bin cutoffs used to define the ALLOWED ($>97\%$ of data) and the CORE ($>80\%$ of data) regions. For each region and amino acid, bins with as many or fewer observations as listed were discarded.

\begin{center}
\footnotesize
\begin{tabular}{lcccccccc}
Residue & ALLOWED & CORE \\
\hline Alanine   & $4$ & $47$ \\
Arginine         & $2$ & $23$ \\
Asparagine       & $2$ & $15$ \\
Aspartate        & $3$ & $20$ \\
Cysteine         & $0$ & $\phantom{0}5$ \\
Glutamate        & $3$ & $34$ \\
Glutamine        & $2$ & $18$ \\
Glycine          & $2$ & $15$ \\
Histidine        & $1$ & $\phantom{0}9$ \\
Isoleucine       & $6$ & $40$ \\
Leucine          & $7$ & $59$ \\
Lysine           & $3$ & $27$ \\
Methionine       & $0$ & $\phantom{0}8$ \\
Phenylalanine    & $2$ & $20$ \\
Proline          & $7$ & $80$ \\
Serine           & $2$ & $27$ \\
Threonine        & $3$ & $33$ \\
Tryptophan       & $0$ & $\phantom{0}8$ \\
Tyrosine         & $2$ & $18$ \\
Valine           & $7$ & $50$ \\
\hline
\end{tabular}
\end{center}

\newpage
\noindent Table S3. Backbone conformation of maximally exposed trimer structures. Multiple rows per residue indicate alternative conformations with comparable solvent exposure.

@@

\newpage
\noindent Table S4. Hydrophobicity scales derived in this work.
\bigskip

@@

\centerline{\includegraphics[width=3.5in]{figures/atom_placement}}
\noindent {\small Schematic drawing of the placement of an atom relative to three reference atoms A, B, and C. Atom C is assumed to be at the origin. The vector from C to B is denoted by $\mathbf{b}$, with coordinates $(x_\mathbf{b}, y_\mathbf{b}, z_\mathbf{b})$. Similarly, the vector from C to A is denoted by $\mathbf{a}$, with coordinates $(x_\mathbf{a}, y_\mathbf{a}, z_\mathbf{a})$. The distance from C to X is $\ell$, the angle between CB and CX is $\theta$, and the dihedral angle between ABC and CX is $\tau$.}
\bigskip
